\chapter{Raspberry Pi-based Solution}
    \section{Rationale}
        \todo{What will make this a good choice?}
        I have chosen to create a solution using the popular Raspberry Pi computer at its core.
        
        \todo{Advantages
            \begin{itemize}
                \item Full featured computer, runs Fedora in particular (dogfooding)
                \item Fairly cheap
                \item Four USBs onboard
                \item Less worry with soldering
                \item Many people are already familiar with it as it's popular among hobbyist projects
            \end{itemize}
        }
        \todo{Disadvantages !!!}
        \blind[2]
    \section{Specification}
        \todo{What, exactly, will the device consist of?}
        The device shall consist of:
        \begin{itemize}
            \item Raspberry Pi~3 Model~B.  Compatibility with Raspberry Pi~2 Model~B may be possible, but not a primary goal.
            \item A compatible 7~inch touchscreen.
            \item A MicroSD card holding the system and several images.
            \item Two male-to-female USB cables.
        \end{itemize}
        
    \section{Construction of a Prototype}
        \todo{A prototype will be built.  This should probably include pictures and a short description of the process}
        \blind[3]
    \section{Simple instructions}
        \todo{These are the final instructions that will be the "result" of the work.  Should they be inlined here?}
        \subsection{Bill of Materials}
            \todo{What is needed to get started - include a table and cost}
            \blind[3]
        \subsection{Step-by-step tutorial}
            \todo{The meat: how to build it from grounds up}
            \todo{Will not be present here, rather as an attachment.}
    \section{Conclusions}
        \todo{Words about if it'll be a good fit, after considering the above}
        \todo{Speeds should be included somewhere in here}
        
        \blind[2]
